Global adjoint tomography -- Model GLAD-M25

### 2018-12-05 main.tex
update plumes and subductions figures

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-4pt]
    \sidesubfloat[]{\includegraphics[width=0.98\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-4pt]
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Aeg.png}\label{fig:a}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Br.png}\label{fig:b}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ha.png}\label{fig:c}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Ne.png}\label{fig:d}}\\[-1pt]
    \sidesubfloat[]{\includegraphics[width=0.88\textwidth]{figures/subductions/Wc.png}\label{fig:a}}\\[-1pt]
    \caption{Vertical cross sections of perturbations of shear wave velocity Vs of plumes.}
\end{figure}
